Simulating High-Dimensional Multivariate Data

### 2020-12-22 030-bigsimr-package.Rmd

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, type = 'pearson', reps=1e6)
```

@@

```{r ch030-rvecRslurm-with-comments, echo=FALSE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)
```

```{r ch030-rvecRslurm, echo=TRUE, eval=FALSE}
library(rslurm)
sjob <- slurm_call(rvec, jobname = 'rvec',
                   alist(n=1e6, rho = rho, margins = margins, type = "spearman"),
                   submit = TRUE)
```

@@

```{r ch030-rvecRslurmMap-comments, echo=FALSE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
set.seed(06202020)
simReps <- 100
rhoList <- replicate(n = simReps, bigsimr::cor_randPSD(d = length(margins)),
                     simplify=FALSE)
sjob <- slurm_map(x = rhoList,
                  f = rvec,
                  jobname = 'rvecMap',
                  n=1e6,
                  margins = margins,
                  type = "spearman",
                  nodes = 4,
                  cpus_per_node = 4,
                  submit = TRUE)

@@

```{r ch030-rvecRslurmMap, echo=TRUE, eval=FALSE}
library(rslurm)
simReps <- 100
rhoList <- replicate(n = simReps, bigsimr::cor_randPSD(d = length(margins)),
                     simplify=FALSE)
sjob <- slurm_map(x = rhoList,
                  f = rvec,
                  jobname = 'rvecMap',
                  n=1e6,
                  margins = margins,
                  type = "spearman",
                  nodes = 4,
                  cpus_per_node = 4,
                  cores = 4,
                  submit = TRUE)
```

@@

```{r ch030-rvecRslurmMapRes, echo=FALSE, eval=FALSE}
list.files('_rslurm_rvecMap', 'results')
res <- rslurm::get_slurm_out(sjob, outtype = 'raw')
rhoHats <- lapply( res, bigsimr::fastCor, method = 'spearman' )
resData <- NULL
simreps <- length(rhoHats)
for (i in 1:simreps){
    tmpRhoHat <- rhoHats[[i]]
    ## average together
    margins
    avgRhoHat <- tmpRhoHat[lower.tri(tmpRhoHat)]
    tmpPair <- paste0( "pair", apply( combn(x = length(margins), 2), 2, paste, collapse = "_" ) )
    tmpResData <- data.frame( simNum=i, rho=rhoList[[i]][1,2], rhoHat=tmpRhoHat[lower.tri(tmpRhoHat)], pair=tmpPair )
    resData <- rbind(resData, tmpResData)
}
## "wrangle" into a tibble
library(tidyverse)
res <- as_tibble(resData)
## save for viz
saveRDS( res, file = 'data/rvecRslurmMapRes.rds' )
## cleanup careful this deletes output also
## cleanup_files(sjob) 
```

>>>>

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, type = 'pearson', reps = 1e6)
```

@@

```{r ch030-rvecRslurm-with-comments, echo=FALSE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n = 1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)
```

```{r ch030-rvecRslurm, echo=TRUE, eval=FALSE}
library(rslurm)
sjob <- slurm_call(rvec, jobname = 'rvec',
                   alist(n = 1e6, 
                         rho = rho, 
                         margins = margins, 
                         type = "spearman"),
                   submit = TRUE)
```

@@

```{r ch030-rvecRslurmMap-comments, echo=FALSE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
set.seed(06202020)
simReps <- 100
rhoList <- replicate(n = simReps, bigsimr::cor_randPSD(d = length(margins)),
                     simplify=FALSE)
sjob <- slurm_map(x = rhoList,
                  f = rvec,
                  jobname = 'rvecMap',
                  n = 1e6,
                  margins = margins,
                  type = "spearman",
                  nodes = 4,
                  cpus_per_node = 4,
                  submit = TRUE)

@@

```{r ch030-rvecRslurmMap, echo=TRUE, eval=FALSE}
library(rslurm)
simReps <- 100
rhoList <- replicate(n = simReps, bigsimr::cor_randPSD(d = length(margins)),
                     simplify=FALSE)
sjob <- slurm_map(x = rhoList,
                  f = rvec,
                  jobname = 'rvecMap',
                  n = 1e6,
                  margins = margins,
                  type = "spearman",
                  nodes = 4,
                  cpus_per_node = 4,
                  cores = 4,
                  submit = TRUE)
```

@@

```{r ch030-rvecRslurmMapRes, echo=FALSE, eval=FALSE}
list.files('_rslurm_rvecMap', 'results')
res <- rslurm::get_slurm_out(sjob, outtype = 'raw')
rhoHats <- lapply(res, bigsimr::fastCor, method = 'spearman')
resData <- NULL
simreps <- length(rhoHats)
for (i in 1:simreps){
    tmpRhoHat <- rhoHats[[i]]
    ## average together
    margins
    avgRhoHat <- tmpRhoHat[lower.tri(tmpRhoHat)]
    tmpPair <- paste0(
      "pair", apply(combn(x = length(margins), 2), 2, paste, collapse = "_")
    )
    tmpResData <- data.frame(
      simNum = i,
      rho    = rhoList[[i]][1,2], 
      rhoHat = tmpRhoHat[lower.tri(tmpRhoHat)], 
      pair   = tmpPair
    )
    resData <- rbind(resData, tmpResData)
}
## "wrangle" into a tibble
library(tidyverse)
res <- as_tibble(resData)
## save for viz
saveRDS(res, file = 'data/rvecRslurmMapRes.rds')
## cleanup careful this deletes output also
## cleanup_files(sjob) 
```

### 2020-12-22 050-examples.Rmd
4th draft. Finalize CMStats2020 talk and fix >= typesetting

$$
\hat{P}( {\bf Y} >= {\bf y_0 } ) = \frac{1}{B} \sum_{b=1}^B I( {\bf Y^{(b) }} >= {\bf y_0 } )
$$

```{r ch050-densityEvaluation, include=FALSE, eval=TRUE, cache=F}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep( 1, d)
pHat <- mean(apply(sim_nbinom,  1,
           function(X, y0=threshold) {
               all(X >= y0)}
           ))
```

@@

```{r ch050-densityEvaluationECHO, echo=TRUE, eval=TRUE, cache=F}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep( 1, d)
mean(apply( sim_nbinom,  1,
           function(X, y0=threshold) {
               all( X >= y0) }
           ))
```

@@

```{r ch050-quadlossECHO, echo=T, eval=F, cache=FALSE}
## Simulate random vectors equal to the sample size
n <- nrow(brca)
## convert outside for faster simulation
nb_Rho_p <- bigsimr::cor_convert( rho = nb_Rho,
                                 from = corType, to = "pearson" )
## ensure PSD
nb_Rho_p <- bigsimr::cor_nearPSD( G = nb_Rho_p )
## create m random vectors and estimate correlation
simRho <- replicate(n = m,
  expr = { tmpSim <- rvec(n = n , nb_Rho_p, nb_margins,
    type = 'pearson', ensure_PSD = FALSE, cores = cores);
    bigsimr::cor_fast( x = tmpSim, method = corType )} ,
simplify = FALSE)
## find quadratic loss at each rep
quadLoss <- unlist( lapply( simRho, rags2ridges::loss,
                           T = nb_Rho, type = "quadratic"))

```

>>>>

$$
\hat{P}( {\bf Y} \ge {\bf y_0 } ) = \frac{1}{B} \sum_{b=1}^B I( {\bf Y^{(b) }} \ge {\bf y_0 } )
$$

```{r ch050-densityEvaluation, include=FALSE, eval=TRUE, cache=F}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep(1, d)
pHat <- mean(apply(sim_nbinom, 1, function(X, y0 = threshold) {
  all(X >= y0)
}))
```

@@

```{r ch050-densityEvaluationECHO, echo=TRUE, eval=TRUE, cache=F}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep(1, d)
mean(apply(sim_nbinom, 1, function(X, y0 = threshold) {
  all( X >= y0)
}))
```

@@

```{r ch050-quadlossECHO, echo=T, eval=F, cache=FALSE}
## Simulate random vectors equal to the sample size
n <- nrow(brca)
## convert outside for faster simulation
nb_Rho_p <- bigsimr::cor_convert( rho = nb_Rho,
                                 from = corType, to = "pearson" )
## ensure PSD
nb_Rho_p <- bigsimr::cor_nearPSD( G = nb_Rho_p )
## create m random vectors and estimate correlation
simRho <- replicate(n = m, expr = {
  tmpSim <- rvec(n = n , nb_Rho_p, nb_margins,
                 type = 'pearson', ensure_PSD = FALSE, cores = cores)
  bigsimr::cor_fast(x = tmpSim, method = corType)
}, simplify = FALSE)
## find quadratic loss at each rep
quadLoss <- sapply(simRho, rags2ridges::loss, T = nb_Rho, type = "quadratic")
```
